Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Complete grammar correctness subsection in the paper

Figure \ref{fields} shows the scatter plot for the sum of numbers of words in summary and description, as well 
as the Time-To-Close for the ticket. We have analysed a total number of 238,286 (all our closed tickets as they 
all have), all having both summaries and descriptions.

@@

>>>>

Figure \ref{fields} shows the scatter plot for the sum of numbers of words in summary and description, as well 
as the Time-To-Close for the ticket. We have analysed a total number of 238,286 tickets, as they all have both 
summaries and descriptions.

@@

Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et. al \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets.

This analysis type is called grammar correctness rather than spelling scores because the range of errors returned 
by Bing Spell Check API are of many types, some of which are:
\begin{itemize}
  \item spelling errors - e.g. Hwo are you today? However, they go much further than a simple character mistyped - for example,
  if one would type Micrsft, it would automatically flag it as a grammar error because it also takes into account a large 
  database of words not in standard dictionaries, but also popular words in the tech world (e.g. company names) or 
  jargon language (e.g. dab dance);
  \item contextual errors - e.g. I ate a book today; even though this is not a misspell, the API will return \emph{book} as 
  a grammar error due to the fact that it is used in the wrong context;
  \item it can detect the wrong usage of a verb tense in a specific context;
  \item it can flag wrong conjugations of verbs;
\end{itemize}

After concatenating the strings for all comments, summary and description, we ran our analysis and then plotted the 
data which is depicted in Figure \ref{grammar}. A correlational analysis revealed a weak positive
relationship with $r = 0.134$ and $p < 0.01$. Thus, our results are statistically significant, implying that 
having more grammar errors in a ticket will increase the Time-To-Close for a ticket and, thus, decrease the quality.

This is expectable as having a text difficult to grasp and understand makes it harder to reason about what needs 
to be done in order to fix a ticket. As it can be seen in the graph, most tickets are concentrated in the range of 
0 to 40 grammar errors per ticket. Having 40 grammar errors in a ticket is quite a large number, considering the fact 
that many tickets don't have comments at all and summary and description are not large in general.

However, we can not automatically change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and typing is no exception. The solution we are proposing implies a 
local, lightweight spell checker that is run automatically as the user types. This tool would not make any external 
calls, so there would be no costs and the load on the server would also be lower. There are already local applications 
that can be used for performing such real-time analysis on the text, one of them being LibreOffice's built-in 
spell checker.
